Rutgers Autonomous Aircraft Team\\Technical Report\\2010 AUVSI UAS Competition

### 2010-05-25 paper/paper.tex
fiddled with some figure placements and some captions. started work on the autopilot description

% We are definitely going to hit the page limit. No more abstract.
%\begin{abstract}
%We will write the abstract after the rest of the paper is finished. 
%If we're really close to the page limit, we may be able to omit it.
%\end{abstract}

@@

We would like to acknowledge
Louis Stumpf, for donating the aircraft that became the \emph{Daedalus};
Jeff Perkins, for his prolific networking and promotion of the team;
Gregg Peters of BP Hobbies for getting us out of numerous binds;
Dave Devries and Michael Maia, of Invensense, for their technical guidance;
Professor Chung-chieh Shan, for overseeing Pat's independent study on the IMU design;
Ivan Seskar, for keeping us (and many other undergrads) in the black; and
Roger Kondos and Brij Pathak, for contributing to the thermopile attitude sensor.

@@

\subsection{Airframe}

@@

The plane, first built out of foam and balsa from long-lost plans in 1986, was accepted graciously, but required quite a bit of work before it was once again flight-worthy. We removed the covering to find water damage and rot which resulted from years of storage. We stripped and rebuilt nearly the entire airframe, adding carbon-fiber reinforcements to the wing in anticipation of increased wing loading due to our payload. Once rebuilt and covered,  the \emph{Daedalus} weighed 19.5 lbs with engine. A full 24oz fuel tank, plus 3.5 lbs electronics payload, would bring the maximum takeoff weight to 25.5lbs.

@@

 \begin{wrapfigure}{r}{0.4\textwidth}
	\includegraphics[width=0.37\textwidth]{../images/daedalus_sandbagtest.jpg}
	\caption{Load testing the underside of the \emph{Daedalus}'s wings. Shown with 16lbs of load.}
	\label{fig:sandbagtest}
\end{wrapfigure}
The plane was carefully supported under the center section, nose, and tail while pre-weighed bags of sand were slowly placed symmetrically and simultaneously on the underside of each wing, starting from the innermost rib.  The \emph{Daedalus} wings supported 64 lbs (250\% of the maximum take-off weight) under static loading.  We also rocked the plane ten degrees from side to side while fully loaded to simulate differential loads during flight. Our post-test structure inspection found no warped members or cracked joints.

@@

\begin{wrapfigure}{l}{0.4\textwidth}
	\centering
	\subfloat[The unfinished \emph{Knight Two}]{\label{fig:knighttwo_construction} 
			\includegraphics[width=0.37\textwidth]{../images/knighttwo_uncovered_outdoors.jpg}}
\\
	\subfloat[A completed 12 Foot Telemaster. Photo Credit: Hobby Lobby] {\label{fig:knighttwo_12ft_telemaster} 
			\includegraphics[width=0.37\textwidth]{../images/telemaster_12ft_hobbylobby.jpg}}
  	\label{fig:knighttwo}
  	\caption[Knight Two]{Knight Two}

\end{wrapfigure}
Someone please detail the outer dimensions. The inner dimensions, space used for flight electronics, space used for payload underneath. Landing gear height. Number of servos and their locations

\subsubsection{Knight Two}

@@

\section{Autopilot}
Our entry uses an autopilot system based off the open source Paparazzi project \cite{paparazziweb}. We ported the airborne code to Linux in order to use a single computer for all of our flight hardware and software.

\subsection{Requirements}

We needed to interface with the following hardware components:
\begin{itemize}
	\setlength{\itemsep}{0cm}
	\setlength{\parskip}{0cm}
	\item GPS
	\item servos
	\item camera
	\item etc.
\end{itemize}

Interfacing with such a large array of devices meant we had to use a ...

\subsection{Hardware}
Description of components selected.
Description of each input, output interface.
\begin{figure}
	\centering
	\includegraphics[width=0.9\textwidth]{../images/hardware_conn_diagram.pdf}
	\caption{Hardware connection diagram for the autopilot and imaging systems. Only one of the 9 axis AHRS and Thermopile Attitude Sensor are used.}
	\label{fig:hardware_conn_diagram}
\end{figure}

\subsection{Software}
\label{sec:autopilot_software}

\begin{figure}
	\centering
	\includegraphics[width=0.9\textwidth]{../images/software_comm_diagram.pdf}
	\caption{Communications diagram}	
	\label{fig:software_comm_diagram}
\end{figure}

\subsection{Ground Station}
Because we based our autopilot software on the Paparazzi project, we were able to make use of their excellent ground control software (GCS) with essentially no modifications.

Detail the capabilities of the Paparazzi GCS.

Figure goes here: Paparazzi ground station screenshot, or whatever. 
\subsection{Tuning and Testing}
PAT

@@

\begin{figure} [H]
	\centering
		\begin{tabular}{ccc}
		\\{\bf altitude (ft)} & {\bf pixel width at 0$^{\circ}$ (in)} & {\bf pixel width at 45$^{\circ}$ (in)} \\
	       100 &       0.38 &       0.54 \\
	       200 &       0.76 &       1.08 \\
	       300 &       1.14 &       1.62 \\
	       400 &       1.52 &       2.16 \\
	       500 &       1.90 &       2.69 \\
		\end{tabular}
		\caption[Pixel Width Mapping]{mapping of altitude to the area each pixel will represent in an image}
		\label{fig:pixelmapping}
\end{figure}

@@

In order to meet the target imaging requirments we needed to add both pan and tilt actuators to the camera. The field of view of our lens is only \degrees(45) by \degrees(34), which is not enough to meet the competition field of view requirements of \degrees(60) vision in each direction.  To address this issue, we designed a pan tilt unit which makes it possible to image the entire hemisphere below the fuselage of the aircraft.

@@

The pan servo is calibrated before installation by mapping servo PWM inputs to a measured angular output at \degrees{30} intervals. Linear interpolation is used to determine PWM outputs which achieve intermediate angles. The tilt servo is calibrated at \degrees{10} intervals, due to its much smaller rotation range. As shown in Figure \ref{fig:pantilt_linkplots}, the angular acceleration of the camera angle linkage (Alpha4) is almost constant compared to the servo arm linkage throughout the range $[0^{\circ}, 135^{\circ}]$. The linkage has been designed to keep the majority of nonlinear rotation outside the camera's range of rotation. Therefore, we can consider the calibrated servo output to be directly related to the camera angle.  The endpoints of the tilt rotation rang are calibrated and enforced in software, because pushing the camera outside this range may damage it.

\subsection{Obtaining Images}

@@

\begin{figure} [H]
	\centering
		\begin{tabular}{rrr}
		 & {\bf Size (KB)} & {\bf Download Time (s)} \\
		 {\bf Original Image} &        1200 &       166.7 \\
		 {\bf Thumbnail} &        125 &       17.4 \\
		 {\bf Crop} &         25 &        3.5 \\
		\end{tabular}
	\caption[Download Times for Images] {size and download time for a full size image vs. a low-resolution thumbnail and a cropped area}
	\label{fig:imagedownloadtimes}
\end{figure}

>>>>

@@

We would like to acknowledge
Louis Stumpf, for donating the aircraft that became the \emph{Daedalus};
Jeff Perkins, for his prolific networking and promotion of the team;
Gregg Peters, of BP Hobbies, for getting us out of numerous binds;
Joe Vanderveer, for keeping a roof over our heads;
Dave Devries and Michael Maia, of Invensense, for their technical guidance and donation of a sensor;
F. Pasolini of ST Micro, for donation of a sensor;
Professor Chung-chieh Shan, for overseeing Pat's independent study on the IMU design;
Ivan Seskar, for keeping us (and many other undergrads) in the black; and
Roger Kondos and Brij Pathak, for contributing to the thermopile attitude sensor.

@@

\newpage
\subsection{Airframe}

@@

The plane, first built out of foam and balsa from long-lost plans in 1986, was accepted graciously, but required quite a bit of work before it was once again flight-worthy. We removed the covering to find water damage and rot which resulted from years of storage. We stripped and rebuilt nearly the entire airframe, adding carbon-fiber reinforcements to the wing in anticipation of increased wing loading due to our payload. Once rebuilt and covered,  the \emph{Daedalus} weighed 19.5 lbs with engine. A full 24oz fuel tank, plus 4lbs electronics payload, would bring the maximum takeoff weight to 25lbs.

@@

 \begin{wrapfigure}{r}{0.4\textwidth}
	\includegraphics[width=0.37\textwidth]{../images/daedalus_sandbagtest.jpg}
	\caption{Load testing the underside of the \emph{Daedalus}'s wings. Shown with 16lbs of load.}
	\label{fig:sandbagtest}
\end{wrapfigure}
The plane was carefully supported under the center section, nose, and tail while pre-weighed bags of sand were slowly placed symmetrically and simultaneously on the underside of each wing, starting from the innermost rib.  The \emph{Daedalus}'s wings supported 64 lbs under static loading. This is 260\% of the maximum take off weight, the force of a 1.5$g$ accelleration multiplied by a 1.73 safety factor.  We also rocked the plane ten degrees from side to side while fully loaded to simulate differential loads during flight. Our post-test structure inspection found no warped members or cracked joints.

@@

\subsubsection{Knight Two}
\begin{wrapfigure}{r}{0.4\textwidth}
	\centering
	\subfloat[The unfinished \emph{Knight Two}]{\label{fig:knighttwo_construction} 
			\includegraphics[width=0.37\textwidth]{../images/knighttwo_uncovered_outdoors.jpg}}
\\
	\subfloat[A completed 12 Foot Telemaster. Photo Credit: Hobby Lobby] {\label{fig:knighttwo_12ft_telemaster} 
			\includegraphics[width=0.37\textwidth]{../images/telemaster_12ft_hobbylobby.jpg}}
  	\label{fig:knighttwo}
  	\caption[Knight Two]{Knight Two}

\end{wrapfigure}

@@

\newpage
\section{Autopilot}
Our entry uses an autopilot system based off the open source Paparazzi project \cite{paparazziweb}. We ported the airborne code to Linux in order to use a single computer for all of our flight hardware and software.

\subsection{Hardware}
\subsubsection{Single Board Computer}
Beagleboard.

\subsubsection{Other Components}
\begin{itemize}
	\setlength{\itemsep}{0cm}
	\setlength{\parskip}{0cm}
	\item GPS: 
	\item Servo Controller:
	\item Autopilot Radio:
	\item Imaging Radio:
	\item Wifi Adapter:
	\item 
\end{itemize}

\begin{figure}
	\centering
	\includegraphics[width=0.9\textwidth]{../images/hardware_conn_diagram.pdf}
	\caption{Hardware connection diagram for the autopilot and imaging systems. Only one of the 9 axis AHRS and Thermopile Attitude Sensor are used.}
	\label{fig:hardware_conn_diagram}
\end{figure}

\subsection{Software}
\label{sec:autopilot_software}
didn't want to be your ghost, didn't want to be anyone's ghost, didn't want to be your ghost, didn't want to be anyone's ghost

but i don't want anyone else
\begin{figure}
	\centering
	\includegraphics[width=0.9\textwidth]{../images/software_comm_diagram.pdf}
	\caption{Communications diagram}	
	\label{fig:software_comm_diagram}
\end{figure}

\subsection{Ground Station}

\begin{wrapfigure}{r}{0.4\textwidth}
	\includegraphics[width=0.37\textwidth]{../images/paparazzi_gcs.jpg}
	\caption{Paparazzi GCS. Image Credit: Paparazzi Wiki\cite{}}
	\label{fig:paparazzi_gcs}
\end{wrapfigure}
Because we based our autopilot software on the Paparazzi project, we were able to make use of their excellent ground control software (GCS) with essentially no modifications. The Paparazzi GCS provides a map interface that allows the operator and competition judges to inspect the aircraft's position to ensure it is within the allowed airspace. It also provides attitude and altitude telemetry, and notification of lost radio contact, so the operator can alert the safety pilot to unsafe operation.

@@

\begin{figure} [H]
	\centering
		\begin{tabular}{ccc}
		\\{\bf altitude (ft)} & {\bf pixel width at 0$^{\circ}$ (in)} & {\bf pixel width at 45$^{\circ}$ (in)} \\
	       100 &       0.38 &       0.54 \\
	       200 &       0.76 &       1.08 \\
	       300 &       1.14 &       1.62 \\
	       400 &       1.52 &       2.16 \\
	       500 &       1.90 &       2.69 \\
		\end{tabular}
		\caption[Pixel Width Mapping]{Linear resolution per pixel as a function of altitude, at directly below flight path and \degrees{45} off flight path}
		\label{fig:pixelmapping}
\end{figure}

@@

In order to meet the target imaging requirments we needed to add both pan and tilt actuators to the camera. The field of view of our lens is only \degrees{45} by \degrees{34}, which is not enough to meet the competition field of view requirements of \degrees{60} vision in each direction.  To address this issue, we designed a pan tilt unit which makes it possible to image the entire hemisphere below the fuselage of the aircraft.

@@

The pan servo is calibrated before installation by mapping servo PWM inputs to a measured angular output at \degrees{30} intervals. Linear interpolation is used to determine PWM outputs which achieve intermediate angles. The tilt servo is calibrated at \degrees{10} intervals, due to its much smaller rotation range. As shown in Figure \ref{fig:pantilt_linkplots}, the angular acceleration of the camera angle linkage (Alpha4) is almost constant compared to the servo arm linkage throughout the range $[0^{\circ}, 135^{\circ}]$. The linkage has been designed to keep the majority of nonlinear rotation outside the camera's range of rotation. Therefore, we can consider the calibrated servo output to be directly related to the camera angle.  The endpoints of the tilt rotation rang are calibrated and enforced in software, because pushing the camera outside this range may damage it.
\newpage
\subsection{Obtaining Images}

@@

\begin{figure} [H]
	\centering
		\begin{tabular}{rrr}
		 & {\bf Size (KB)} & {\bf Download Time (s)} \\
		 {\bf Original Image} &        1200 &       166.7 \\
		 {\bf Thumbnail} &        125 &       17.4 \\
		 {\bf Crop} &         25 &        3.5 \\
		\end{tabular}
	\caption[Download Times for Images] {Size and download time for a full size image vs. a low-resolution thumbnail and a cropped area}
	\label{fig:imagedownloadtimes}
\end{figure}
